## How to use this syllabus {-}


This syllabus website is dynamic. If you catch typos, errors, please issue a pull request with the fixes. Unless otherwise indicidated, all the policies apply to all of my courses.


To navigate this syllabus collection, use the table of contents on the left side of the screen. You can open or close the table of contents using the hamburger icon (horizontal bars) at the top of the document. There are also additional icons at the top of the document that allow you to search the document, change the size, font, or color scheme of the page. Please note that the syllabus may be updated throughout the semester, but students are only bound to the policies in place when they signed their syllabus.



# Attributions {-}

This collection of syllabii leans on the work and ideas of other people. I have done my best to document the origin of the materials and ideas. In particular, I have noted those people whose work has been a major contribution as well as those who have additional contributions. You can view a record of any changes made to the syllabus by checking the [edit history in the git repository.](https://github.com/smasongarrison/Syllabi/commits/main)

## Major Attributions  {-}

* Jenny Bryan's ([jennybryan.org](https://jennybryan.org)) [STAT 545][stat-545]


## Additional Attributions  {-}

**Select lecture notes from:**

* Jenny Bryan's ([jennybryan.org](https://jennybryan.org/)) [STAT 545](https://stat545.com/)
* [David Funder's Personality Puzzle](https://wwnorton.com/books/The-Personality-Puzzle/)
* Anthony Albano's [Course Notes on "Introduction to Educational and Psychological Measurement"](https://www.thetaminusb.com/intro-measurement-r/)
* R. Biswas-Diener & E. Diener (Eds), Noba textbook series: Psychology. Champaign, IL: DEF publishers. Retrieved from [noba](https://nobaproject.com/)

# License {-#license}

This work is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-sa/4.0/).

<!-- <center>
<i class="fab fa-creative-commons fa-2x"></i><i class="fab fa-creative-commons-by fa-2x"></i><i class="fab fa-creative-commons-sa fa-2x"></i>
</center>
 -->
 
* This information is a human-readable summary of (and not a substitute for) the license.
Please see https://creativecommons.org/licenses/by-sa/4.0/legalcode for the full legal text.*

**You are free to:**

- **Share**---copy and redistribute the material in any medium or
  format

- **Remix**---remix, transform, and build upon the material for any
  purpose, even commercially.

The licensor cannot revoke these freedoms as long as you follow the
license terms.

**Under the following terms:**

- **Attribution**---You must give appropriate credit, provide a link
  to the license, and indicate if changes were made. You may do so in
  any reasonable manner, but not in any way that suggests the licensor
  endorses you or your use.
  
- **ShareAlike**---If you remix, transform, or build upon the material, you must distribute your contributions under the same license as the original. 

- **No additional restrictions**---You may not apply legal terms or
  technological measures that legally restrict others from doing
  anything the license permits.

**Notices:**

You do not have to comply with the license for elements of the
material in the public domain or where your use is permitted by an
applicable exception or limitation.

No warranties are given. The license may not give you all of the
permissions necessary for your intended use. For example, other rights
such as publicity, privacy, or moral rights may limit how you use the
material.

```{r include = FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), "bookdown", "knitr", "rmarkdown"
), "packages.bib")
```




# Colophon {-}

This syllabus was written in [bookdown](http://bookdown.org/) inside [RStudio](http://www.rstudio.com/ide/). The [website][web] is hosted with [github](https://www.github.com), The complete source is available from [github][git].

The book style adapted from [Desirée De Leon](https://desiree.rbind.io/).

This version of the syllabus was built with:


```{r message = FALSE,error=TRUE, warning = FALSE, echo = FALSE}
# needed because new_session is set to true in _bookdown.yml
library(tidyverse)
all_pkgs <- renv::dependencies(path = "DESCRIPTION") %>%
  pull(Package)

session <- devtools::session_info(pkgs = all_pkgs)

session$platform
```

Along with these packages:


```{r message = FALSE,error=TRUE, warning = FALSE, echo = FALSE}
if (knitr::is_latex_output()) {
  session$packages %>%
    select(package, loadedversion, date, source) %>%
    knitr::kable(booktabs = TRUE)
} else {
  session$packages %>%
    select(package, loadedversion, date, source) %>%
    DT::datatable(
      rownames = FALSE,
      class = "cell-border stripe",
      filter = list(position = "top"),
      options = list(
        pageLength =
          nrow(session$packages),
        autoWidth = TRUE,
        bInfo = FALSE,
        paging = FALSE
      )
    )
}
```

The R session information when compiling this book is shown below:

```{r include=FALSE}
# only show versions of very relevant packages
sessionInfo <- function() {
  lapply(c("shiny", "miniUI"), loadNamespace)
  res <- utils::sessionInfo()
  loaded <- res$loadedOnly
  res$loadedOnly <- loaded[intersect(names(loaded), c(
    "bookdown", "knitr", "rmarkdown", "shiny", "htmltools", "tools", "miniUI"
  ))]
  res$BLAS <- res$LAPACK <- NULL
  res
}
```

```{r}
sessionInfo()
```

```{r links, child="links.md"}
```
