```{r include = FALSE}
source("common.R")
library(webshot)
```

# Accommodations Policy

If you are (or become) disabled (in any capacity, permanently, or temporarily), and need accommodations in class, reading, or any other work in this course, please contact me to discuss your specific needs as soon as possible. 
Under my favorite civil rights legislation, the Americans with Disabilities Act as amended you are legally entitled to reasonable accommodations for disabilities. In fact, Section 504 of the Rehabilitation Act of 1973, the [Americans with Disabilities Act (ADA) of 1990](https://beta.ada.gov/), and the [ADA Amendments Act (ADAAA) of 2008](https://en.wikipedia.org/wiki/ADA_Amendments_Act_of_2008) all prohibit discrimination against individuals with disabilities.
I will do everything in my capacity as your professor to ensure that you receive those accommodations. 

Students who need reasonable accommodations for disabilities also should contact the Center for Learning, Access, and Student Success  (118 Reynolda Hall, 336-758-5929,  [class.wfu.edu](https://class.wfu.edu/)). You can request accommodations through the [student portal (olympic.accessiblelearning.com/WFU/)](https://olympic.accessiblelearning.com/WFU/) These accommodations are not retroactive. Therefore, I strongly encourage you to use those accommodations.  As a member of CLASS's faculty advising board, I am happy to connect you with CLASS and talk to you more if you have questions. (However, please note that I am a quantitative Psychologist, not a clinical psychologist. My expertise stems from lived experience.)

Do not feel guilty about using them. 
You rightfully deserve them, in the legal, moral, and ethical sense. 
These accommodations are there so that you can be your best possible self. 

```{r, echo=FALSE}
library(tweetrmd) #... embedding tweets
# Error in tweet_blockquote(tweet_url = tweet_url, maxwidth = maxwidth,  : 
#  Forbidden (HTTP 403).
if(TRUE){
try_include_tweet("https://twitter.com/bluntshovels/status/1463275576337129480")
}
```


## Self-Advocacy

At Wake Forest and at many other places, the expectation is that you will self-advocate for yourselves and know exactly what you need. Is that a good expectation? Is that a good model? Is that equitable? I have thoughts... regardless, that is the current state of the world. Accordingly, you will have to advocate for what you need. If this process seems daunting, please talk to me! Regardless, I am happy to talk with you about this process and to share my own experiences.


```{r, echo=FALSE}

try_include_tweet("https://twitter.com/Rasheeradiara/status/1532760383500472326")
try_include_tweet("https://twitter.com/theADHDacademic/status/1458876178580881410")
```

As a student, you may not know what accommodations work best for you. Or you may find that your current accommodations don't work like they used to. 

As you journey thru your career, you may find that you need different kinds of accommodations. Or at least that has been my experience... There are numerous resources for ideas. 
My personal favorite is [JAN](https://askjan.org/). Technically, JAN (Job Accommodation Network) is focused on employment and jobs. 
However, I still have found this to be a wonderful resource for ideas. 
You can [search for accommodation ideas](https://askjan.org/soar.cfm) by [specific](https://askjan.org/a-to-z.cfm):

  - disability,
  - limitation,
  - task,
  - topic, or
  - accommodation.

## Resources

* [Frequently Asked Questions from WFU CLASS](https://class.wfu.edu/frequently-asked-questions-students/)
* [JAN](https://askjan.org/)
* [WFU Self-advocacy handout](https://docs.google.com/document/d/1X44zJyTz8-s9t6IXw0bII2DCFiOk1NR2MRfTi8wBiIc/)
* [College Foundation of North Carolina's Know Your Rights](https://www.cfnc.org/plan-your-future/plan-for-college/students-with-disabilities/know-your-rights/)

# Classroom Climate

I aim to create a learning environment for my students that supports a diversity of thoughts, perspectives, and experiences, and honors your identities (including but not limited to race, ethnicity, sex, gender, gender-identity, class, culture, sexual orientation, religion, disability, political affiliation, military status). To help accomplish this:

- If you have a name or set of pronouns that differ from those that appear in your official records, please let me know!

- If you feel like your performance in the class is being impacted by your experiences outside of class, please don't hesitate to come and talk with me. I can direct you to resources

- I (like many people) am still in the process of learning about diverse perspectives and identities. If something was said in class (by anyone) that made you feel uncomfortable, please talk to me about it. 

- If you reached here in the syllabus, e-mail me a picture of a cat. If you do it before the end of the first week, you get a small bonus. (And even if its after the first week, feel free to still send me a cat picture.)

<!--
## Statements

### From the psychology department
The Psychology Department values, respects, and celebrates the experiences, beliefs, and practices stemming from varied cultures and circumstances (emphasizing, but not limited to, those from historically underrepresented groups),and our deep commitment to diversity, equity, and inclusion plays out through coursework, programming by majors, and research. 

### How I'd expand it
The Psychology Department values, respects, and celebrates the experiences, beliefs, and practices stemming from varied cultures and circumstances ( emphasizing, but not limited to, those from marginalized groups, including those historically underrepresented). We center our department around our deep commitment to diversity, equity, inclusion, and access. That deep commitment plays out through coursework, programming by majors, service, outreach, and research. 
 -->
