# 210: Methods in Psych Research {#statsminor .unnumbered}

```{r setup, include=FALSE}
source("scheduler.R")
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
first_day <- as.Date("2025-08-25")
cache <- F
number_of_classes <- 29
number_of_weeks <- 16
num_exams <- 3
num_counted_exams <- 2
num_assignments <- 2
num_counted_assignments <- 1

####
#devtools::install_github("crsh/citr")
library(tidyverse)
library(citr)
library(RefManageR)
bib <- ReadBib("book.bib")
bib <- c(bib, as.BibEntry(citation()))
bib[length(bib)]$key = "Rcite"

topicvanderbilt <- c(
  "Introduction", 
  "Getting Ready to Do Statistical Analysis",
  "Describing Data with R",
  "Univariate Distributions",
  "Test 1",
  "Bivariate Distributions",
  "Probability Theory",#  "Spring Break",#  "",
  "Binomials and other sampling distributions", 
  "Spring Break", 
  "Hypothesis Testing",
  "Inferences about means",
  "Special Topics", 
  "Test 3", 
  "Applications in R",
  "Applications in R",
  "Applications in R", 
  "NA",
  "NA"
  )
topic_v2 =c(
  "Introduction", # intro, science process
  "Statistical Foundations", # Variability Variability
  "Describing Data with R",
  "Univariate Distributions",
  "Bivariate Distributions",
  "Probability Theory",
  "Binomials and other sampling distributions",#  "Spring Break",#  "",
  "Hypothesis Testing", 
  "Spring Break", 
  "T-Tests",
  "Regression",
  "Causal Inference",
  "ANOVA",
  "Applications in R",
  "Applications in R",
  "Review", 
  "NA",
  "NA"
  )

topic <- c(
  "What are Research Methods?", # Week 1
  "Getting Ready to Do Statistical Analysis", # Week 2
  "Describing Data with R", # Week 3
  "Univariate Distributions", # Week 4
  "Bivariate Distributions", # Week 5
  "Probability Theory", # Week 6
  "Binomials and Other Sampling Distributions", # Week 7
  "Hypothesis Testing", # Week 8
#  "Spring Break", # Week 10
  "T-Tests", # Week 11
  "F-Tests and ANOVA", # Week 12
  "Causal Inference", # Week 13
  "Experimental Designs", # Week 14
  "Ethics and Reproducibility", # Week 15
  "Special Topics", # Week 16
  "Putting it all together", # Week 16
  "Finals" # Week 17
)

#topic=topicvanderbilt 
classschedule <- data.frame(module = 1:number_of_weeks)
classschedule$start <- advdate(first_day,classschedule$module,weekday_due = "m")
classschedule$topic <- topic[1:number_of_weeks]
classschedule$week <- advdate(first_day,classschedule$module)
classschedule$milestones <- as.character(NA)

exams<-c(6,12,16)
# factory fire
#exams[1:2]<-c(6,13)
assignments<-c(8,15)
#assignments[1]<-c(9)
classschedule$milestones[exams] <- "Exam"
classschedule$milestones[assignments] <- "Assignment"

```

## Course Description {.unnumbered}

Methods in Psychological Research introduces statistics and research design for students minoring in psychology. Prereq: P—PSY 151 (D, QR)

This course is designed to help students develop the conceptual background and practical skills necessary to evaluate the statistics encountered in their coursework and in everyday life. It emphasizes selection, application, and interpretation. Topics to be covered include statistical inference, probability distributions, sampling, hypothesis testing, and correlation. The goal will be to go beyond rote memorization of abstract formulas and for students to develop an appreciation for the critical role that statistics plays in psychological science.

## Required Materials {.unnumbered}

Morling, (5th Edition) Research Methods in Psychology <https://seagull.wwnorton.com/researchpsych5>

## Course Assignments {.unnumbered}

### Grading Policy {.unnumbered}

```{r child = './common/content/grading_curve.Xmd'}
```

### Quizzes {.unnumbered}

There will be 14 multiple-choice reading quizzes (effectively these are weekly). The best 13 out of 14 quiz grades will be used to determine your total quiz grade. You can drop 1 of the quizzes for any reason.

### Exams {.unnumbered}

There will be `r num_exams` exams. The best `r num_counted_exams` out of `r num_exams` exam grades will be used to determine your total exam grade. You can drop 1 of the exams for any reason.

#### Exams Dates {.unnumbered}

-   Exam 1: Friday, `r advdate(first_day, exams[1], weekday_due="f")`

-   Exam 2: Friday, `r advdate(first_day, exams[2], weekday_due="f")`

-   Exam 3: During Finals, `r advdate(first_day, exams[3], weekday_due="f")`

### Short Assignments {.unnumbered}

There will be `r num_assignments` short assignments in this course. These assignments will allow you to incorporate some of your own interests into the course. Such interests could be related to your career, another class you're taking, a hobby you're exploring, or some other random fancy. They will typically be approximately two (2) pages. I will provide more specific written guidelines at least two weeks before each assignment is due.

The best `r num_counted_assignments` out of `r num_assignments` short assignments will be used to determine your total short assignments. You can skip one of the assignments for any reason.

#### Assignment Dates {.unnumbered}

-   Assignment 1: Friday, `r advdate(first_day, assignments[1], weekday_due="f")`: Qualitative Critique 1

-   Assignment 2: Friday, `r advdate(first_day, assignments[2], weekday_due="f")`: Qualitative Critique 2

## Engagement Activities {.unnumbered}

There will be multiple engagement activities in this course. These activities will allow you engage with the material for each module. Details about the specific activities will be provided on canvas. Students must complete two activities per module.

## Grading Weighting {.unnumbered}

-   200 points of your grade will be determined by your best `r num_counted_exams` exams.
-   50 points of your grade will be determined by your best `r num_counted_assignments` assignment(s).
-   20 points of your grade will be determined by your engagement.
-   30 points of your grade will be determined by your best 13 quizzes.

## Schedule {.unnumbered}

```{r message = FALSE, warning = FALSE, echo = FALSE}

classschedule %>% 
  DT::datatable(rownames = FALSE,
                class = 'cell-border stripe',
                #filter = list(position = 'top'),
                options = list(pageLength = nrow(classschedule$module), 
                           autoWidth = FALSE,
                           bInfo = FALSE,
                           paging = FALSE))
```

```{=html}
<!---
Schedule
-->
```
```{=html}
<!---
## `r advdate(first_day, 1, topic)`

- Monday: First Day of Class / Introduction
- Thursday: First Day of Class

## `r advdate(first_day, 2, topic)`

- Tuesday: Research Design (Chapter 9)
- Thursday: Sampling Theory (Chapter 8) / Measurement in the Social/Behavioral Sciences 


##  `r advdate(first_day, 3, topic)` 

- Tuesday: Describing Data Graphically with R

- Wednesday (Sep 05, 2018)
    - Last day to drop a class (with a paper drop form) with no entry on the record
    - Last day to add a class & register for pass/fail status using paper forms 
- Thursday: Describing Data Numerically with R



##  `r advdate(first_day, 4, topic)`

- Tuesday: Univariate Distributions (Chapter 1/2)
- Thursday: Standardization, z-scores, and the normal distribution  (Chapter 3)

##  `r advdate(first_day, 5, topic)`

- Tuesday: Test 1 Review

- Thursday: Test 1

##  `r advdate(first_day, 6, topic)`

- Tuesday: Bivariate Distributions (Chapter 4)

- Thursday: Correlation (Chapter 5)

##  `r advdate(first_day, 7, topic)` 

- Thursday: Probability Theory (Chapter 12) 

##  `r advdate(first_day, 8, topic)`

- Tuesday: More Probability Theory (Chapter 13) 

- Thursday: Review

##  `r advdate(first_day, 9, topic)`

- Tuesday: Test 2

- Thursday No Class (Fall Break Oct 18-19)
- Friday (Oct 19, 2018)
    - Last day undergraduate students may withdraw from fall semester classes
    - Last day to change from pass/fail to graded status in a fall semester class

##  `r advdate(first_day, 10, topic)`

- Tuesday: The Logic of Hypothesis Testing Hypotheses, Errors (Chapters 16-19)

- Thursday: t-tests

##  `r advdate(first_day, 11, topic)`

- Tuesday: Applying t-tests and ANOVA (Chapters 20 & 21)

- Thursday: More Analysis of Variance   (Chapters 24 & 27)

##  `r advdate(first_day, 12, topic)`

- Tuesday: Subverting the Research Process

- Thursday: Causal Inference

## `r advdate(first_day, 13, topic)`

- Tuesday: Review

- Wednesday: Alternative Test Date

- Thursday: Test 3

##  `r advdate(first_day, 14, topic)`

- Monday: Cross-Cultural Psychology
- Wednesday: Cross-Cultural Psychology
- Friday: Cross-Cultural Psychology


##  `r advdate(first_day, 15, topic)`

- Tuesday: Translating Research Questions into R

- Thursday: Addressing Statistical Questions in R


##  `r advdate(first_day, 16, topic)` 

- Tuesday: Addressing Statistical Questions in R
- Thursday: Last Day of Class 
- Friday: Extra Credit Due at 7pm

## Final Exam 

- TBD on DEC TBD

# References

-->
```
