# 255: Personality {-#personality}

```{r setup, include=FALSE}
dayone <- as.Date("2022-08-22")
cache=F
number_of_classes=29
number_of_weeks=17

source("scheduler.R")
####
#devtools::install_github("crsh/citr")
library(tidyverse)
library(citr)
library(RefManageR)

bib <- ReadBib("book.bib")
bib <- c(bib, as.BibEntry(citation()))
bib[length(bib)]$key = "Rcite"

topic = c(
  "What is Personality", 
  "Personality Research Methods",
  "Assessment, Evaluation, and Ethics",
  "Trait Approach and Personality Judgment",
  "Big Five",
  "Personality over the Lifespan",# 
  "Biological Approaches to Psychology", 
  "Behavior Genetics",
  "Evolutionary Psychology", 
  "Cross-Cultural Psychology",
  "Freud", 
  "Psychoanalysis After Freud", 
  "Personality Processes and Positive Psych",
  "Thanksgiving Break!",
  "Personality and Health"
  )



classschedule <- data.frame(module = 1:number_of_weeks)
classschedule$start <- advdate(dayone,classschedule$module,assignment = "m")
classschedule$topic <- topic[1:number_of_weeks]
classschedule$week <- advdate(dayone,classschedule$module)

classschedule$milestones <- as.character(NA)

exams<-c(5,12,17)

assignments<-c(7,16)

classschedule$milestones[exams] <- "Exam"
classschedule$milestones[assignments] <- "Assignment"
```



## Course Description   {-}

This class provides a survey of theory and research on the structure and function of human personality, with attention to the relationship to cognition, emotion, motivation, and behavior. It requires P-PSY 151. In addition, we will discuss other individual differences, such as intelligence.

### Broad goals for the course:   {-}
- 1. The first is for you to understand what personality psychologists think. We will cover classic and current theories, research, and applications of Personality psychology.
- 2. The second is for you to learn how personality psychologists study their field scientifically. We will discuss the procedures used to test theories and to study issues related to personality.
- 3. The third is to (hopefully) recognize some relevance of personality psychology for your personal and/or professional life.


## Required Materials   {-}

```{r, echo = FALSE, results="asis"} 
bib[sort(c("funder_personality_2016"))]
``` 


## Course Assignments   {-}

### Quizzes   {-}

There will be 15 multiple-choice reading quizzes (effectively these are weekly). The best 12 out of 15 quiz grades will be used to determine your total quiz grade.  You can drop 3 of the quizzes for any reason.

### Exams   {-}

There will be 3 exams. The best 2 out of 3 exam grades will be used to determine your total exam grade.  You can drop 1 of the exams for any reason.


#### Exams Dates   {-}

- Exam 1: Friday, `r advdate(dayone, exams[1], assignment="f")`

- Exam 2: Friday, `r advdate(dayone, exams[2], assignment="f")`

- Exam 3: During Finals, `r advdate(dayone, exams[3], assignment="f")`


### Short Assignments   {-}

There will be two (2) short assignments in this course. These assignments will allow you to incorporate some of your own interests into the course. Such interests could be related to your career, another class you're taking, a hobby you're exploring, or some other random fancy. They will typically be approximately two (2) pages. I will provide more specific written guidelines at least two weeks before each assignment is due.


The best one (1) out of two (2) short assignments will be used to determine your total short assignments.  You can skip one of the assignments for any reason.


#### Short Assignment Dates   {-}

- Assignment 1: Friday, `r advdate(dayone, assignments[1], assignment="f")`: Critique of an online personality test.

- Assignment 2: Friday, `r advdate(dayone, assignments[2], assignment="f")`: Critique of a personality-related media article OR a personality-related YouTube video.

<!--
- Assignment 3: Friday, `r advdate(dayone, assignments[3], assignment="f")`: Critique of a personality-related YouTube video.

-->

### Engagement Activities   {-}

There will be multiple engagement activities in this course. These activities will allow you engage with the material for each module. Details about the specific activities will be provided on canvas. Students must complete two activities per module. For students in the blended section, they can attend their weekly in-person session and count it as an engagement activity.


## Grading Policy   {-}

```{r child = './common/content/grading.Xmd'}
```

### Weighting   {-}

- 200 points of your grade will be determined by your best two (2) exams.
- 100 points of your grade will be determined by your best two short assignments.
- 30 points of your grade will be determined by your engagement.
- 120 points of your grade will be determined by your best 12 quizzes





## Schedule {-}

```{r message = FALSE, warning = FALSE, echo = FALSE}

classschedule %>% 
  DT::datatable(rownames = FALSE,
                class = 'cell-border stripe',
                #filter = list(position = 'top'),
                options = list(pageLength = nrow(classschedule$module), 
                           autoWidth = FALSE,
                           bInfo = FALSE,
                           paging = FALSE))
```





