# 255: Personality {-#personality}

```{r setup, include=FALSE}
first_day <- as.Date("2022-08-22")
cache <- F
number_of_classes <- 29
number_of_weeks <- 16
num_quizzes <- 6
num_counted_quizzes <- 5
num_assignments <- 3
num_counted_assignments <- 2
source("scheduler.R")
####
#devtools::install_github("crsh/citr")
library(tidyverse)
library(citr)
library(RefManageR)

bib <- ReadBib("book.bib")
bib <- c(bib, as.BibEntry(citation()))
bib[length(bib)]$key = "Rcite"

topic = c(
  "What is Personality", 
  "Personality Research Methods",
  "Assessment, Evaluation, and Ethics",
  "Trait Approach and Personality Judgment",
  "Big Five",
  "Personality over the Lifespan",# 
  "Biological Approaches to Psychology", 
  "Behavior Genetics",
  "Evolutionary Psychology", 
  "Cross-Cultural Psychology",
  "Freud", 
  "Psychoanalysis After Freud", 
  "Personality Processes and Positive Psych",
  "Thanksgiving Break!",
  "Personality and Health"
  )
exams_week <- c(3,6,10,13,15,16)
assignments_week <- c(7,12,16)
classschedule <- create_classschedule(first_day = first_day,
                     number_of_weeks = number_of_weeks,
                     weekday_due = "m",
                     topic = topic,
                     exams_week= exams_week,
                     assignments_week= assignments_week)

if(length(exams_week) != num_quizzes){
  stop("The number of exams must match the number of quizzes")
}
if(length(assignments_week) != num_assignments){
  stop("The number of assignments must match the number of assignments")
}
```





## Course Description   {-}

This class provides a survey of theory and research on the structure and function of human personality, with attention to the relationship to cognition, emotion, motivation, and behavior. It requires P-PSY 151. In addition, we will discuss other individual differences, such as intelligence.

### Broad goals for the course:   {-}
- 1. The first is for you to understand what personality psychologists think. We will cover classic and current theories, research, and applications of Personality psychology.
- 2. The second is for you to learn how personality psychologists study their field scientifically. We will discuss the procedures used to test theories and to study issues related to personality.
- 3. The third is to (hopefully) recognize some relevance of personality psychology for your personal and professional life.


## Required Materials   {-}

```{r, echo = FALSE, results="asis"} 
bib[sort(c("funder_personality_2016"))]
``` 


## Course Assignments   {-}

### Quizzes    {-}
There will be `r num_quizzes` quizzes in this course. The best `r num_counted_quizzes` out of `r num_quizzes` quizzes grades will be used to determine your total quiz grade.  You can drop any of the quizzes for any reason BUT YOU MUST PASS THE LAST Quiz ( that is held during the university scheduled final exam period).  If you do not pass the final quiz, your score on that quiz will count as one of your `r num_counted_quizzes` grades. If you do pass the final quiz, then the best `r num_counted_quizzes` grades will be used (irrespective of your score on the final quiz).



#### Quiz Dates   {-}

- Quiz 1: Friday, `r advdate(first_day, exams_week[1], weekday_due="f")`

- Quiz 2: Friday, `r advdate(first_day, exams_week[2], weekday_due="f")`

- Quiz 3: Friday, `r advdate(first_day, exams_week[3], weekday_due="f")`

- Quiz 4: Friday, `r advdate(first_day, exams_week[4], weekday_due="f")`

- Quiz 5: Friday, `r advdate(first_day, exams_week[5], weekday_due="f")`

- Quiz 6: During Finals, `r advdate(first_day, exams_week[6], weekday_due="f")`


### Short Assignments   {-}

There will be  `r num_assignments` short assignments in this course. These assignments will allow you to incorporate some of your own interests into the course. Such interests could be related to your career, another class you're taking, a hobby you're exploring, or some other random fancy. They will typically be approximately two (2) pages. I will provide more specific written guidelines at least two weeks before each assignment is due.


The best  `r num_count_assignments` out of  `r num_assignments` short assignments will be used to determine your total short assignments.  You can skip one of the assignments for any reason.


#### Short Assignment Dates   {-}

- Assignment 1: Friday, `r advdate(first_day, assignments_week[1], weekday_due="f")`: Critique of an online personality test.

- Assignment 2: Friday, `r advdate(first_day, assignments_week[2], weekday_due="f")`: Critique of a personality-related media article.

- Assignment 3: Friday, `r advdate(first_day, assignments_week[3], weekday_due="f")`: Critique of a personality-related YouTube video.

### Engagement Activities   {-}

There will be multiple engagement activities in this course. These activities will allow you engage with the material for each module. Details about the specific activities will be provided on canvas. Students must complete two activities per module. For students in the blended section, they can attend their weekly in-person session and count it as an engagement activity.


## Grading Policy   {-}

```{r child = './common/content/grading.Xmd'}
```

### Weighting   {-}

- `r num_counted_quizzes*30` points of your grade will be determined by your best `r num_counted_quizzes` quizzes
    - The final is not optional.
- 25 points of your grade will be determined by completing engagement activities.
- `r num_counted_assignments*50` points of your grade will be determined by your best two short assignments.



## Schedule {-}

```{r message = FALSE, warning = FALSE, echo = FALSE}

classschedule %>% 
  DT::datatable(rownames = FALSE,
                class = 'cell-border stripe',
                #filter = list(position = 'top'),
                options = list(pageLength = nrow(classschedule$module),
                               autoWidth = FALSE,
                               bInfo = FALSE,
                               paging = FALSE))
```

