# 310: Methods in Psychological Research {-#statsminor}

```{r setup, include=FALSE}
source("scheduler.R")
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
dayone <- as.Date("2022-01-10")
cache=F
number_of_classes=29
number_of_weeks=15

####
#devtools::install_github("crsh/citr")
library(tidyverse)
library(citr)
library(RefManageR)



bib <- ReadBib("book.bib")
bib <- c(bib, as.BibEntry(citation()))
bib[length(bib)]$key = "Rcite"


topicvanderbilt =c(
  "Introduction", 
  "Getting Ready to Do Statistical Analysis",
  "Describing Data with R",
  "Univariate Distributions",
  "Test 1",
  "Bivariate Distributions",
  "Probability Theory",#  "Spring Break",#  "",
  "Binomials and other sampling distributions", 
  "Test 2", 
  "Hypothesis Testing",
  "Inferences about means",
  "Special Topics", 
  "Test 3", 
  "Applications in R",
  "Applications in R",
  "Applications in R" 
  )

 topic=topicvanderbilt 
classschedule <- data.frame(module = 1:number_of_weeks)
classschedule$start <- advdate(dayone,classschedule$module,assignment = "m")
classschedule$topic <- topic[1:number_of_weeks]
classschedule$week <- advdate(dayone,classschedule$module)

```



## Course Description  {-}

Methods in Psychological Research introduces statistics and research design for students minoring in psychology. Prereq: P—PSY 151 (D, QR)

This course is designed to help students develop the conceptual background and practical skills necessary to evaluate the statistics encountered in their coursework and in everyday life. It emphasizes selection, application, and interpretation. Topics to be covered include statistical inference, probability distributions, sampling, hypothesis testing, and correlation. The goal will be to go beyond rote memorization of abstract formulas and for students to develop an appreciation for the critical role that statistics plays in psychological science.


### Broad goals for the course:  {-}
- 1. To understand the selection, computation, and interpretation of descriptive and inferential
statistics
- 2. To learn how to use and interpret R (R Core Team 2018).


## Required Materials  {-}

Morling, Research Methods in Psychology https://wwnorton.com/books/9780393893724


## Course Assignments  {-}


## Schedule  {-}



```{r message = FALSE, warning = FALSE, echo = FALSE}

classschedule %>% 
  DT::datatable(rownames = FALSE,
                class = 'cell-border stripe',
                #filter = list(position = 'top'),
                options = list(pageLength = nrow(classschedule$module), 
                           autoWidth = FALSE,
                           bInfo = FALSE,
                           paging = FALSE))
```


<!---
Schedule
-->
<!---
## `r advdate(dayone, 1, topic)`

- Monday: First Day of Class / Introduction
- Thursday: First Day of Class

## `r advdate(dayone, 2, topic)`

- Tuesday: Research Design (Chapter 9)
- Thursday: Sampling Theory (Chapter 8) / Measurement in the Social/Behavioral Sciences 


##  `r advdate(dayone, 3, topic)` 

- Tuesday: Describing Data Graphically with R

- Wednesday (Sep 05, 2018)
    - Last day to drop a class (with a paper drop form) with no entry on the record
    - Last day to add a class & register for pass/fail status using paper forms 
- Thursday: Describing Data Numerically with R



##  `r advdate(dayone, 4, topic)`

- Tuesday: Univariate Distributions (Chapter 1/2)
- Thursday: Standardization, z-scores, and the normal distribution	(Chapter 3)

##  `r advdate(dayone, 5, topic)`

- Tuesday: Test 1 Review

- Thursday: Test 1

##  `r advdate(dayone, 6, topic)`

- Tuesday: Bivariate Distributions (Chapter 4)

- Thursday: Correlation	(Chapter 5)

##  `r advdate(dayone, 7, topic)` 

- Thursday: Probability Theory (Chapter 12) 

##  `r advdate(dayone, 8, topic)`

- Tuesday: More Probability Theory (Chapter 13) 

- Thursday: Review

##  `r advdate(dayone, 9, topic)`

- Tuesday: Test 2

- Thursday No Class (Fall Break Oct 18-19)
- Friday (Oct 19, 2018)
    - Last day undergraduate students may withdraw from fall semester classes
    - Last day to change from pass/fail to graded status in a fall semester class

##  `r advdate(dayone, 10, topic)`

- Tuesday: The Logic of Hypothesis Testing Hypotheses, Errors (Chapters 16-19)

- Thursday: t-tests

##  `r advdate(dayone, 11, topic)`

- Tuesday: Applying t-tests and ANOVA (Chapters 20 & 21)

- Thursday: More Analysis of Variance	(Chapters 24 & 27)

##  `r advdate(dayone, 12, topic)`

- Tuesday: Subverting the Research Process

- Thursday: Causal Inference

## `r advdate(dayone, 13, topic)`

- Tuesday: Review

- Wednesday: Alternative Test Date

- Thursday: Test 3

##  `r advdate(dayone, 14, topic)`

- Monday: Cross-Cultural Psychology
- Wednesday: Cross-Cultural Psychology
- Friday: Cross-Cultural Psychology


##  `r advdate(dayone, 15, topic)`

- Tuesday: Translating Research Questions into R

- Thursday: Addressing Statistical Questions in R


##  `r advdate(dayone, 16, topic)` 

- Tuesday: Addressing Statistical Questions in R
- Thursday: Last Day of Class 
- Friday: Extra Credit Due at 7pm

## Final Exam 

- TBD on DEC TBD

# References

-->
