---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    latex_engine: pdflatex
    template: ./common/style/svm-latex-syllabus.tex
    
bibliography: library.bib

geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt

title: "PSY 362. Psychological Testing"

date: '`r format(Sys.time(), "%B %d, %Y")`'

author: S. Mason Garrison
email: "GarrisSM@wfu.edu"


officehours: By Appointment \href{https://calendly.com/smasongarrison/}{\small\tt calendly.com/smasongarrison}
office: "GREENE 438"
officev: Zoom \href{https://wakeforest-university.zoom.us/my/smasongarrison}{\tiny\tt wakeforest-university.zoom.us/my/smasongarrison}

classroom: Canvas
classdelivery: "Asynchronous"
web: \href{https://wakeforest.instructure.com/courses/28913}{\tt wakeforest.instructure.com/courses/28913} 



header-includes:
   - \linespread{1.05}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
mon <- as.Date("2020-08-24")
cache=F
number_of_classes=29
number_of_weeks=15
advdate <- function(obj, adv, topic = NULL,assignment=NULL) {
 tmon <- obj + 7*(adv-1)
 ttue <- obj + 1 + 7*(adv-1)
 twed <- obj + 2 + 7*(adv-1)
 tthu <- obj + 3 + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 ttue <- format(ttue, format="%m/%d")
 twed <- format(twed, format="%m/%d")
 tthu <- format(tthu, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)

 if (is.null(topic)&is.null(assignment)){
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 } else if(!is.null(assignment)){if(assignment %in% c("Friday","friday","f","fri")){
  tmp <- paste0(tfri)
 } else if(assignment %in% c("Tuesday","tues","t","Tue")){
  tmp <- paste0(ttue)
 }else if(assignment %in% c("wednesday","Wednesday","w","wed","W")){
  tmp <- paste0(twed)
 } else if(assignment %in% c("thursday","Thursday","thurs","r","R")){
  tmp <- paste0(tthu)
 } else if(assignment %in% c("monday","Monday","m")){
  tmp <- paste0(tmon)
 }
 }
 else{ 
   tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri, " : ", topic[adv])}
 return(tmp)
}

####
#devtools::install_github("crsh/citr")
library(tidyverse)
library(citr)
library(RefManageR)



bib <- ReadBib("library.bib")
bib <- c(bib, as.BibEntry(citation()))
bib[length(bib)]$key = "Rcite"

topic=c(
  "Introduction", 
  "Historical, Ethical, and Social Considerations in Testing",
  "Norms and the Meaning of Test Scores",
  "Reliability",
  "Validity",
  "More Validity", 
  "Item Analysis", 
  "Test 1",
  "Spring Break",
  "Individual Differences",
  "Ability Testing",
  "Personality Testing", 
  "Measuring Interests and Attitudes",
  "Other Assessment Techniques", 
  "Modern Development and Applications of Testing", 
  "Review"
  )
  
  



```

# Course Description

This course provides an overview of the development and nature of psychological tests with applications to school counseling, business, and clinical practice. The purpose of the course is to provide students with an understanding of the principles of measurement as applied to group standardized measures of achievement, special aptitude, intelligence, personality, interests and distress for use in counseling.  Format will consist primarily of lectures along with group participation activities. 


```{r child = './common/content/doingwell_irl.Rmd'}
```
## Course Objectives:
- To acquaint you with the fundamental vocabulary and logic of psychological measurement and behavioral assessment.
- To develop your capacity for critical judgment of the adequacy of measures purported to assess behavior in the role of theory development.
- To acquaint you with some of the relevant literature in personality assessment, psychometric theory and practice, and methods of observing and measuring behavior.
- To instill in you an appreciation of and an interest in the principles and methods of psychometric theory in general and behavior assessment in particular.
- This course is not designed to make you into an accomplished psychometist (one who gives tests) nor is it designed to make you a skilled psychometrician (one who constructs tests), nor will it give you "hands on" experience with psychometric computer programs. Rather it is aimed to allow you to understand the fundamental theoretical issues concerning both the psychometrist and the psychometrician.
- Because modern psychometrics and statistics may be done using open source software such as R, examples will be presented in R. Instructions for installing and using R for psychometrics are available here.

# Materials
## Texts
### Required

```{r, echo = FALSE, results="asis"} 
bib[sort(c("anastasi1997"))]
``` 


#### How to use the required text:

The text [@anastasi1997] is intended to supplement the lectures. The lectures don't follow the order of chapters in the text and the text covers some material that won't be covered in the lectures, i.e., not all the information in each chapter is perfectly pertinent to the course requirements.


# Course Assignments

## Tests 
There will be X tests in this course.  The best 2 out of 3 exam grades will be used to determine your total exam grade.  You can drop any of the exams for any reason BUT YOU MUST PASS THE LAST EXAM (held at TBD on Dec TBD).  If you do not pass the final exam, your score on that exam will count as one of your 2 grades. If you do pass the final exam, then the best 2 grades will be used (irrespective of your score on the final exam).


### Test Dates

- Test 1: Friday, `r advdate(mon, 5, assignment="f")`

- Test 2: Friday, `r advdate(mon, 10, assignment="f")`

- Test 3: During Finals Week


## Short Assignments 
There will be three (3) short assignments in this course. These assignments will allow you to incorporate some of your own interests into the course. Such interests could be related to your career, another class you're taking, a hobby you're exploring, or some other random fancy. They will typically be approximately two (2) pages. I will provide more specific written guidelines at least two weeks before each assignment is due.


The best two (2) out of three (3) short assignments will be used to determine your total short assignments.  You can skip one of the assignments for any reason.
### Short Assignment Dates

- Assignment 1: Friday, `r advdate(mon, 4, assignment="f")`: Critique of an online personality test.

- Assignment 2: Friday, `r advdate(mon, 8, assignment="f")`: Critique of a personality-related media article.

- Assignment 3: Friday, `r advdate(mon, 12, assignment="f")`: Critique of a personality-related YouTube video.

## Engagement Activities

There will be multiple engagement activities in this course. These activities will allow you engage with the material for each module. Details about the specific activities will be provided on canvas. Students must complete two activities per module. For students in the blended section, they can attend their weekly in-person session and count it as an engagement activity.



# Course Policies
## Grading Policy

```{r child = './common/content/grading.Rmd'}
```

## Grading Weighting

- 200 points of your grade will be determined by two (2) tests.
- 100 points of your grade will be determined by two (2) short assignments.
- 50 points of your grade will be determined by your attendance and participation in class. Generally, ask questions and answer them.


### Test Dates

- Test 1: Thursday, `r advdate(mon, 8, assignment="t")`

- Test 2: During Finals Week, TBD


## Short assignments 
There will be two (2) assignments in this course. I will provide more specific written guidelines at least two weeks before each assignment is due.


### Short Assignment Dates

- Assignment 1: Tuesday, `r advdate(mon, 7, assignment="t")`.

- Assignment 2: Thursday, `r advdate(mon, 13, assignment="t")`.



## Class Presence and Participation.

Class presence and participation points are given to encourage your active class participation and discussion.  You will be rewarded with a perfect score as long as you frequently come to class and actively contribute to the class discussion during recitations and lectures. 


### Excused absences

I recognize that occasions arise during the academic year that merit the excused absence of a student from a scheduled class or laboratory during which an examination, quiz, or other graded exercise is given. Examples include participation in sponsored university activities (e.g., debate team, varsity sports), observance of officially designated religious holidays, serious personal problems (e.g., serious illness, death of a member of the student's family), and matters relating to the student's academic training (e.g., graduate or professional school interviews). Conflicts arising from personal travel plans or social obligations do not qualify as excused absences. 

Except in the case of true emergencies, a possible excused absence should be discussed with me as far in advance as possible - you should not assume that an excused absence will automatically be granted. This discussion should occur via email.  If you also discuss your situation verbally, please send a summary of the discussion via email to me.  An unexcused absence will result in a zero for any graded work that should have been performed for or during the missed class.  


## Academic Dishonesty Policy

All work submitted for credit must be the student's own and is subject to the provisions of the Wake Forest Honor Code. Details can be found at the Student Conduct web site:
[studentconduct. wfu.edu/honor-system-wfu](https://studentconduct.wfu.edu/honor-system-wfu/).


## Accommodations Policy

If you are (or become) learning, sensory, or physically disabled, and need special course accommodations in class, reading, or any other work in this course, please contact me to discuss your specific needs as soon as possible. Students who need reasonable accommodations for disabilities also should contact the Learning Assistance Center \& Disability Services [lac.wfu.edu](https://lac.wfu.edu/).


# Classroom Climate

I aim to create a learning environment for my students that supports a diversity of thoughts, perspectives, and experiences, and honors your identities (including race, gender, class, sexuality, religion, ability, political affiliation, etc.) To help accomplish this:

- If you have a name and/or set of pronouns that differ from those that appear in your official records, please let me know!

- If you feel like your performance in the class is being impacted by your experiences outside of class, please don't hesitate to come and talk with me. I want to be a resource for you. Remember that you can also submit anonymous feedback (which will lead to me making a general announcement to the class, if necessary to address your concerns).

- I (like many people) am still in the process of learning about diverse perspectives and identities. If something was said in class (by anyone) that made you feel uncomfortable, please talk to me about it. (Again, anonymous feedback is always an option).


## Department Statement
The Psychology Department values, respects, and celebrates the experiences, beliefs, and practices stemming from varied cultures and circumstances (emphasizing, but not limited to, those from historically underrepresented groups), and our deep commitment to diversity, equity, and inclusion plays out through coursework, programming by majors, and research. 


# Tentative Class Schedule

This syllabus is intended to give the student guidance in what may be covered during the semester and will be followed as closely as possible. However, I reserve the right to modify, supplement and make changes as the course needs arise.


## `r advdate(mon, 1, topic)`

- Tuesday: Chapter 1
- Thursday: Chapter 2

## `r advdate(mon, 2, topic)`

- Tuesday: Chapter 18
- Thursday: Chapter 18

##  `r advdate(mon, 3, topic)` 

- Tuesday: Chapter 3 "Last day to add full-term class"
- Thursday: Chapter 3

##  `r advdate(mon, 4, topic)`

- Tuesday: Chapter 4
- Thursday: Chapter 4

##  `r advdate(mon, 5, topic)`

- Tuesday: Chapter 5 + 6
- Thursday: Chapter 5 + 6 

##  `r advdate(mon, 6, topic)`

- Tuesday: Chapter 6  "Last day to drop full-term class"
- Thursday: Chapter 9 

##  `r advdate(mon, 7, topic)` 

- Tuesday: Chapter 7 (Assignment 1 Due)
- Thursday: Chapter 7

##  `r advdate(mon, 8, topic)`

- Tuesday: Review 
- Thursday: Exam 1

##  `r advdate(mon, 9, topic)`

- Tuesday: No class
- Thursday: No class 

##  `r advdate(mon, 10, topic)`

- Tuesday: Selected readings
- Thursday: Chapter 10

##  `r advdate(mon, 11, topic)`

- Monday: Last day to drop with a grade of "W"
- Tuesday: Chapter 11
- Thursday: Chapter 12

##  `r advdate(mon, 12, topic)`

- Tuesday: Chapter 13
- Thursday: Chapter 13 

## `r advdate(mon, 13, topic)`

- Tuesday: Chapter 14
- Thursday: Chapter 14 (Assignment 2 Due)

##  `r advdate(mon, 14, topic)`

- Tuesday: Chapter 15
- Thursday: Chapter 16

##  `r advdate(mon, 15, topic)`

- Tuesday: Supplemental reading
- Thursday: Supplemental reading

##  `r advdate(mon, 16, topic)` 

- Tuesday: Review

## Final Exam 

- TBD

# References
