\documentclass[11pt,]{article}
\usepackage[margin=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}
\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center
\newcommand{\blankline}{\quad\pagebreak[2]}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{longtable,booktabs}

\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\titleformat*{\subsubsection}{\normalsize\itshape}

\usepackage{titling}
\setlength{\droptitle}{-.25cm}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{\footnotesize PSY 362. Psychological Testing -- December 15, 2020}
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}

\fancypagestyle{firststyle}
{
\renewcommand{\headrulewidth}{0pt}%
   \fancyhf{}
   \fancyfoot[C]{\small \thepage/\pageref*{LastPage}}
}

%\def\labelitemi{--}
%\usepackage{enumitem}
%\setitemize[0]{leftmargin=25pt}
%\setenumerate[0]{leftmargin=25pt}




\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={ ()},
             pdfkeywords = {},
            pdftitle={PSY 362. Psychological Testing},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls


\setcounter{secnumdepth}{0}

\usepackage{longtable}




\usepackage{setspace}

\title{PSY 362. Psychological Testing}
\author{S. Mason Garrison}

\date{December 15, 2020}


\begin{document}

		\maketitle
	

		\thispagestyle{firststyle}

%	\thispagestyle{empty}


\noindent \begin{tabular*}{\textwidth}{ @{\extracolsep{\fill}} lr @{\extracolsep{\fill}}}
\hline\\
    &  Class Room: Canvas
%
\\\hline\\
%
 Web: \href{https://wakeforest.instructure.com/courses/28913}{\tt wakeforest.instructure.com/courses/28913}&  \\ %wraps \url{} around any url
 %wraps \url{} around any url
 %wraps \url{} around any url
&  \\
Professor: S. Mason Garrison \\

E-mail: \texttt{\href{mailto:GarrisSM@wfu.edu}{\nolinkurl{GarrisSM@wfu.edu}}}  \\

WFU Office: GREENE 438   \\
Virtual Office: Zoom
\href{https://wakeforest-university.zoom.us/my/smasongarrison}{\tiny\tt wakeforest-university.zoom.us/my/smasongarrison}   \\
Hours: By Appointment
\href{https://calendly.com/smasongarrison/}{\small\tt calendly.com/smasongarrison}  \\


	&  \\
	\hline
\end{tabular*}

\vspace{2mm}

\hypertarget{course-description}{%
\section{Course Description}\label{course-description}}

This course provides an overview of the development and nature of
psychological tests with applications to school counseling, business,
and clinical practice. The purpose of the course is to provide students
with an understanding of the principles of measurement as applied to
group standardized measures of achievement, special aptitude,
intelligence, personality, interests and distress for use in counseling.
Format will consist primarily of lectures along with group participation
activities.

\hypertarget{course-objectives}{%
\subsection{Course Objectives:}\label{course-objectives}}

\begin{itemize}
\tightlist
\item
  To acquaint you with the fundamental vocabulary and logic of
  psychological measurement and behavioral assessment.
\item
  To develop your capacity for critical judgment of the adequacy of
  measures purported to assess behavior in the role of theory
  development.
\item
  To acquaint you with some of the relevant literature in personality
  assessment, psychometric theory and practice, and methods of observing
  and measuring behavior.
\item
  To instill in you an appreciation of and an interest in the principles
  and methods of psychometric theory in general and behavior assessment
  in particular.
\item
  This course is not designed to make you into an accomplished
  psychometist (one who gives tests) nor is it designed to make you a
  skilled psychometrician (one who constructs tests), nor will it give
  you ``hands on'' experience with psychometric computer programs.
  Rather it is aimed to allow you to understand the fundamental
  theoretical issues concerning both the psychometrist and the
  psychometrician.
\item
  Because modern psychometrics and statistics may be done using open
  source software such as R, examples will be presented in R.
\end{itemize}

\hypertarget{materials}{%
\section{Materials}\label{materials}}

\hypertarget{texts}{%
\subsection{Texts}\label{texts}}

\hypertarget{required}{%
\subsubsection{Required}\label{required}}

{[}1{]} A. Anastasi and A. Urbina. \emph{Psychological testing}. Upper
Saddle River, New Jersey: Prentice-Hall, 1997. ISBN: 0-02-303020-8.

\hypertarget{how-to-use-the-required-text}{%
\paragraph{How to use the required
text:}\label{how-to-use-the-required-text}}

The text (Anastasi and Urbina 1997) is intended to supplement the
lectures. The lectures don't follow the order of chapters in the text
and the text covers some material that won't be covered in the lectures,
i.e., not all the information in each chapter is perfectly pertinent to
the course requirements.

\hypertarget{course-assignments}{%
\section{Course Assignments}\label{course-assignments}}

\hypertarget{tests}{%
\subsection{Tests}\label{tests}}

There will be X tests in this course. The best 2 out of 3 exam grades
will be used to determine your total exam grade. You can drop any of the
exams for any reason BUT YOU MUST PASS THE LAST EXAM (held at TBD on Dec
TBD). If you do not pass the final exam, your score on that exam will
count as one of your 2 grades. If you do pass the final exam, then the
best 2 grades will be used (irrespective of your score on the final
exam).

\hypertarget{test-dates}{%
\subsubsection{Test Dates}\label{test-dates}}

\begin{itemize}
\item
  Test 1: Friday, 02/26
\item
  Test 2: Friday, 04/02
\item
  Test 3: During Finals Week
\end{itemize}

\hypertarget{short-assignments}{%
\subsection{Short Assignments}\label{short-assignments}}

There will be three (3) short assignments in this course. These
assignments will allow you to incorporate some of your own interests
into the course. Such interests could be related to your career, another
class you're taking, a hobby you're exploring, or some other random
fancy. They will typically be approximately two (2) pages. I will
provide more specific written guidelines at least two weeks before each
assignment is due.

The best two (2) out of three (3) short assignments will be used to
determine your total short assignments. You can skip one of the
assignments for any reason. \#\#\# Short Assignment Dates

\begin{itemize}
\item
  Assignment 1: Friday, 02/19: Critique of an online personality test.
\item
  Assignment 2: Friday, 03/19: Critique of a personality-related media
  article.
\item
  Assignment 3: Friday, 04/16: Critique of a personality-related YouTube
  video.
\end{itemize}

\hypertarget{engagement-activities}{%
\subsection{Engagement Activities}\label{engagement-activities}}

There will be multiple engagement activities in this course. These
activities will allow you engage with the material for each module.
Details about the specific activities will be provided on canvas.
Students must complete two activities per module.

\hypertarget{course-assignments-1}{%
\section{Course Assignments}\label{course-assignments-1}}

\hypertarget{grading-policy}{%
\subsection{Grading Policy}\label{grading-policy}}

Typically, an A- is defined as 90\% of the highest point total in the
class, B- as 80\% of that total, C- as 70 and D- as 60\%. I may shift
these values down to provide a better fit to the actual point
distribution. By scaling to a percentage of the highest point total in
the class, each student has a much better chance of receiving higher
grades than if no re-scaling were done. This curve can only help your
grade.

The full table is provided below:

\begin{longtable}[]{@{}lr@{}}
\caption{Full Table}\tabularnewline
\toprule
Letter & Cutoff\tabularnewline
\midrule
\endfirsthead
\toprule
Letter & Cutoff\tabularnewline
\midrule
\endhead
A & 0.95\tabularnewline
A- & 0.90\tabularnewline
B+ & 0.87\tabularnewline
B & 0.82\tabularnewline
B- & 0.80\tabularnewline
C+ & 0.77\tabularnewline
C & 0.72\tabularnewline
C- & 0.70\tabularnewline
D+ & 0.67\tabularnewline
D & 0.62\tabularnewline
D- & 0.60\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{curve-projections}{%
\subsubsection{Curve Projections}\label{curve-projections}}

Unsurprisingly, students have many questions about the curve in this
class. For tests and other assignments, I try to provide a projected
letter grade. This projected letter grade is there to give you a sense
of what your score \emph{would} be if I implemented the class curve on
this particular assignment. It is a projection. It is not a guarantee.
These projected letter grades are not incorporated into your final
grade. Trust me, you do not want me to curve by assignment.

\hypertarget{late-work}{%
\subsubsection{Late Work}\label{late-work}}

Be sure to pay close attention to deadlines. Unless you have a
compelling reason and instructor pre-approval, there will be no make-up
assignments, quizzes, tests, or late work accepted. See the policy on
excused absences for specifics on instructor pre-approval.

It is the responsibility of the student to ensure that the instructor
has received the assignment by the established due date and to ensure
that the assignment submitted is the complete and correct version.
Unless otherwise specificied, all work must be submitted through Canvas.

\hypertarget{grading-weighting}{%
\subsubsection{Grading Weighting}\label{grading-weighting}}

\begin{itemize}
\tightlist
\item
  200 points of your grade will be determined by two (2) tests.
\item
  100 points of your grade will be determined by two (2) short
  assignments.
\item
  50 points of your grade will be determined by your engagement.
  Generally, ask questions and answer them.
\end{itemize}

\hypertarget{test-dates-1}{%
\subsubsection{Test Dates}\label{test-dates-1}}

\begin{itemize}
\item
  Test 1: Thursday, 03/16
\item
  Test 2: During Finals Week, TBD
\end{itemize}

\hypertarget{short-assignments-1}{%
\subsection{Short assignments}\label{short-assignments-1}}

There will be two (2) assignments in this course. I will provide more
specific written guidelines at least two weeks before each assignment is
due.

\hypertarget{short-assignment-dates}{%
\subsubsection{Short Assignment Dates}\label{short-assignment-dates}}

\begin{itemize}
\item
  Assignment 1: Tuesday, 03/09.
\item
  Assignment 2: Thursday, 04/20.
\end{itemize}

\hypertarget{course-policies}{%
\section{Course Policies}\label{course-policies}}

\hypertarget{class-presence-and-participation.}{%
\subsection{Class Presence and
Participation.}\label{class-presence-and-participation.}}

In previous semesters, I have had a deliberately hardline attendance
policy. In the light of the public health crisis, I have done away with
the this policy, as it doesn't align with my general philosophy of
treating students as junior colleagues. The student who misses a class
meeting is responsible for any assignments and/or announcements made.

Class presence and participation points are given to encourage your
active engagement with the material. Specific instructions for
engagement, can be found on Canvas. In general, you will be rewarded
with a perfect score as long as you engage meaningfully and
intentionally with the material and your peers.

\hypertarget{excused-absences-and-extension-policy}{%
\subsection{Excused absences and extension
policy}\label{excused-absences-and-extension-policy}}

As a reasonable and empathetic human, I recognize that life happens.
There will be times when your outside life conflicts with scheduled
class events. These life events can be any of the obvious things
(sports, religious holidays, illness, interviews, etc), but they can
also be the less obvious, like spending the entire night looking for
your lost pet. My general approach is to work with you. You just need to
let me know ahead of time. Conflicts arising from personal travel plans
or social obligations do not qualify as excused absences, unless those
commitments were set before this course began. If that is the case,
please let me know within the first \textbf{two weeks} of class.

Except in the case of \emph{true} emergencies, a possible excused
absence should be discussed with me as far in advance as possible and
\emph{must} occur beforehand. You should not assume that an excused
absence will automatically be granted -- but you may assume that I am a
reasonable, empathetic person. This discussion should occur via email.
If you also discuss your situation verbally, please send a summary of
the discussion via email to me.\\
An unexcused absence will result in a zero for any graded work that
should have been performed for or during the missed class.

\hypertarget{academic-dishonesty-policy}{%
\subsection{Academic Dishonesty
Policy}\label{academic-dishonesty-policy}}

All work submitted for credit must be the student's own and is subject
to the provisions of the Wake Forest Honor Code. Details can be found at
the Student Conduct web site:
\href{https://studentconduct.wfu.edu/honor-system-wfu/}{studentconduct.
wfu.edu/honor-system-wfu}.

Unless I have explicitly stated otherwise, every assessment is closed to
outside resources (including, but not limited to books, notes, phones,
people). Ignorance of the honor code and assignment instructions is not
an acceptable explanation and/or defense.

It is \emph{ALWAYS} academic dishonesty to share test questions, post
course materials on any third-party websites, or to work together on
tests. And frankly, it is really obvious in Canvas when you work
together. I literally wrote a R program that checks for working
together, using a non-parametric statistic method.

Violations of this policy result in a zero for the assignment and
possible additional penalties, including, but not limited to a referral
to honor council, failing the class, a ban from all extra-credit
assignments, and no longer being able to drop assignments.

\hypertarget{accommodations-policy}{%
\subsection{Accommodations Policy}\label{accommodations-policy}}

If you are (or become) disabled (in any capacity, permanently, or
temporarily), and need accommodations in class, reading, or any other
work in this course, please contact me to discuss your specific needs as
soon as possible. Under the Americans with Disabilities Act, you are
legally entitled to reasonable accommodations for disabilities. I will
do everything in my capacity as your Professor to ensure that you
receive those accommodations.

Students who need reasonable accommodations for disabilities also should
contact the Learning Assistance Center \& Disability Services
\href{https://lac.wfu.edu/}{lac.wfu.edu}. These accommodations are not
retroactive. Therefore, I strongly encourage you to use those
accommodations. You rightfully deserve them, both in the legal, moral,
and ethical sense.

\hypertarget{communication}{%
\subsection{Communication}\label{communication}}

You are expected to read every LMS announcement, message, and email; as
well as view the media embedded within those communications. Students
are expected to check e-mail on a frequent and regular basis in order to
stay current with University-related communications, recognizing that
certain communications may be time-critical. At minimum, you should be
checking your communications within 48 hours. Ignorance of a class
communication is not grounds for an excused absence or extension.

\hypertarget{self-advocacy}{%
\subsubsection{Self Advocacy}\label{self-advocacy}}

If you are struggling in this class, please talk to me. Do not assume
that I know what is going on in your life. Talk to me and tell me what
you need.

\hypertarget{grading-questions}{%
\subsubsection{Grading Questions}\label{grading-questions}}

Please send any questions about grades in writing via email within
\emph{two} weeks after the assignment is returned. If I erred in scoring
or in calculating the grade, I will happily update the record.
Otherwise, I will be most receptive toward questions framed in terms of
your learning (rather than simply your performance), as research has
shown that focusing overly on extrinsic rewards (like grades) is likely
to lead to all sorts of outcomes that I don't wish for you (lower
interest in the course material, lower learning, lower enjoyment).

\hypertarget{instructor-availability}{%
\subsection{Instructor Availability}\label{instructor-availability}}

I am readily accessible during business hours (9:00AM-5:30PM;
Monday-Friday) via email/ LMS/ zoom/ carrier pigeon. Outside those
hours, I do not typically respond to messages, in order to devote time
to my family, rest, and living my life. Messages received during these
times will receive attention once I am back online. Otherwise you can
expect to receive a response to your message within 12 to 24 hours,
often much sooner. If you do not hear back after 24 hours, please
follow-up with me.

I have given out my cell-phone number, in the case of \emph{true}
emergencies. Please be mindful that poor planning on your part does not
constitute an emergency for me.

\hypertarget{is-it-an-true-emergency}{%
\subsubsection{Is it an true emergency?}\label{is-it-an-true-emergency}}

How do you know if it is a true emergency?

\begin{itemize}
\tightlist
\item
  Ask yourself, would a reasonable person consider this situation an
  emergency?
\item
  How would the situation change if you waited a until morning?
\item
  Could this situation have been prevented by starting earlier?
\item
  Would Professor Mason really want to know about this situation
  \emph{right} now?
\item
  If you were in Professor Mason's shoes, would you consider this an
  emergency?
\end{itemize}

\hypertarget{public-health-in-the-age-of-covid-19}{%
\section{Public Health in the age of
COVID-19}\label{public-health-in-the-age-of-covid-19}}

Each of us shares responsibility for the health and safety of all in a
learning space. Maintaining a consistent six feet of distance; wearing a
face covering; limiting our gathering sizes; and isolating or
quarantining when ill or exposed to someone with the virus are Wake
Forest University directives and policies we all must follow. Students
are encouraged to visit the Our Way Forward website
(ourwayforward.wfu.edu) to stay informed about the latest guidance and
review the
\href{https://studentconduct.wfu.edu/undergraduate-student-handbook/minimum_expectations/public-health-emergency-addendum/}{Public
Health Emergency Addendum to the Student Code of Conduct}.

Specifically, in this room, we will mitigate the risks of virus transfer
and take care of our community by abiding by the following safety
directives:

\begin{itemize}
\tightlist
\item
  maintain six feet of distance at all times when feasible.
\item
  wear a face covering for the entirety of class. This face covering
  should cover your mouth and your nose, and adhere to
  \href{https://drive.google.com/file/d/1Hc_yL-Pzec2TdfPTgrC18Cb96vympsbI/view}{our
  University face covering policy} (no face shields without masks; no
  neck gaiters; no bandanas; and no masks, including N95, with a one-way
  valve).
\item
  stay out of class when sick or after being exposed to someone who is
  sick.
\end{itemize}

In this class, any student who does not follow these requirements will
be asked once to follow the safety directives. I will offer you a mask
or ask you to find one. If you do not comply, I will ask you to leave
the class for that day.
\href{https://cm.maxient.com/reportingform.php?WakeForestUniv\&layout_id=40}{I
will also refer the matter to the COVID-19 compliance reporting system.}
Possible disciplinary actions may follow as described in the Wake Forest
University Undergraduate Student Conduct Code Public Health Emergency
Addendum.

\hypertarget{classroom-climate}{%
\section{Classroom Climate}\label{classroom-climate}}

I aim to create a learning environment for my students that supports a
diversity of thoughts, perspectives, and experiences, and honors your
identities (including race, ethnicaity, sex, gender, gender-identify,
class, sexual orientation, religion, ability, political affiliation,
etc.) To help accomplish this:

\begin{itemize}
\item
  If you have a name and/or set of pronouns that differ from those that
  appear in your official records, please let me know!
\item
  If you feel like your performance in the class is being impacted by
  your experiences outside of class, please don't hesitate to come and
  talk with me. I want to be a resource for you.
\item
  I (like many people) am still in the process of learning about diverse
  perspectives and identities. If something was said in class (by
  anyone) that made you feel uncomfortable, please talk to me about it.
\item
  If you reached here in the syllabus, e-mail me a picture of a cat. If
  you do it before the end of the first week, you get a small bonus.
\end{itemize}

\hypertarget{department-statement}{%
\subsection{Department Statement}\label{department-statement}}

The Psychology Department values, respects, and celebrates the
experiences, beliefs, and practices stemming from varied cultures and
circumstances (emphasizing, but not limited to, those from historically
underrepresented groups), and our deep commitment to diversity, equity,
and inclusion plays out through coursework, programming by majors, and
research.

\hypertarget{to-do-well-in-the-course}{%
\section{To do well in the course}\label{to-do-well-in-the-course}}

To do well in the course, you should read the assigned material before
class and re-read previously assigned material as the course progresses.
By reading the text before class you will be better prepared to ask
questions and integrate the content of lectures with what was presented
in the text. For synchronous classes, be sure to attend all lectures and
arrive on time. For asynchronous classes be sure to watch all the video
lectures and don't leave them until the last minute. Each topic builds
directly on the previous one. Thus, if you miss one lecture or zip
through a video, you run the risk of being completely lost in the next
lecture.

\hypertarget{important-information-for-college-and-this-course}{%
\subsection{Important Information for College and This
Course:}\label{important-information-for-college-and-this-course}}

In addition, many professors have implicit (\emph{i.e.}, unspoken)
expectations for college classes. I'm going to explicitly state some of
those unspoken expectations. I suspect that your other professors have
similar expectations -- so this information will help you in your other
classes.

Asynchronous courses put the onus on \textbf{YOU} to keep up with the
work. You are not guaranteed any reminders throughout the semester. Go
to the schedule included here and put it in your calendar. You should
also:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  check course announcements on Canvas often, and
\item
  check your email tied to Canvas often.
\end{enumerate}

Email and canvas is how I communicate with you, and I will not
continually repeat myself in emails after I have already posted or sent
the information.

High school and college are different. In high school, you may have been
permitted to turn in work as late as you like, to redo assignments or
quizzes until you were satisfied, and to complete extra credit work.
This is not the case in this college-level course. Unless explicitly
stated, there are no late assignments, make-up work, redoing of
assignments, or extra credit. These are course policies; they are not
opportunities for negotiation. Although I am always happy to explain the
reasoning and calculus behind my policies, they are not negotiable.

There is also a prevalent attitude of, ``it doesn't hurt to ask.'' Yes,
it does. If I have already made clear my policies and expectations,
asking me to violate them damages your credibility as a student. One day
you may ask for something that is truly reasonable given an emergency
situation, but by then your reputation will precede you. Do not be ``the
boy who cried wolf;'' it is not a respected position.

Finally, you should understand that college is not a fee-for-service
arrangement. You are not paying me. You are paying tuition to a
University for all kinds of things, very little of which actually ``pays
my salary.'' Salaries are more commonly paid out of government funds,
including grants. You start with a zero in college courses and earn your
points from there. I am not ``giving'' you grades or ``taking away''
points. You have nothing to begin with and earn your own score based on
what you do and how well you do it (not simply on effort). What I offer
you is an opportunity for education, not a grade.

\hypertarget{tentative-class-schedule}{%
\section{Tentative Class Schedule}\label{tentative-class-schedule}}

This syllabus is intended to give the student guidance in what may be
covered during the semester and will be followed as closely as possible.
Dates for tests and assignments won't change, barring extraordinary
events. However, I reserve the right to modify, supplement and make
changes as the course needs arise. I try to avoid changes to the
syllabus. Nevertheless, if changes occur, I will only make changes that
are less burdensome and more advantageous to the students.

\hypertarget{week-01-0125---0129-introduction}{%
\subsection{Week 01, 01/25 - 01/29 :
Introduction}\label{week-01-0125---0129-introduction}}

\begin{itemize}
\tightlist
\item
  Tuesday: Chapter 1
\item
  Thursday: Chapter 2
\end{itemize}

\hypertarget{week-02-0201---0205-historical-ethical-and-social-considerations-in-testing}{%
\subsection{Week 02, 02/01 - 02/05 : Historical, Ethical, and Social
Considerations in
Testing}\label{week-02-0201---0205-historical-ethical-and-social-considerations-in-testing}}

\begin{itemize}
\tightlist
\item
  Tuesday: Chapter 18
\item
  Thursday: Chapter 18
\end{itemize}

\hypertarget{week-03-0208---0212-norms-and-the-meaning-of-test-scores}{%
\subsection{Week 03, 02/08 - 02/12 : Norms and the Meaning of Test
Scores}\label{week-03-0208---0212-norms-and-the-meaning-of-test-scores}}

\begin{itemize}
\tightlist
\item
  Tuesday: Chapter 3 ``Last day to add full-term class''
\item
  Thursday: Chapter 3
\end{itemize}

\hypertarget{week-04-0215---0219-reliability}{%
\subsection{Week 04, 02/15 - 02/19 :
Reliability}\label{week-04-0215---0219-reliability}}

\begin{itemize}
\tightlist
\item
  Tuesday: Chapter 4
\item
  Thursday: Chapter 4
\end{itemize}

\hypertarget{week-05-0222---0226-validity}{%
\subsection{Week 05, 02/22 - 02/26 :
Validity}\label{week-05-0222---0226-validity}}

\begin{itemize}
\tightlist
\item
  Tuesday: Chapter 5 + 6
\item
  Thursday: Chapter 5 + 6
\end{itemize}

\hypertarget{week-06-0301---0305-more-validity}{%
\subsection{Week 06, 03/01 - 03/05 : More
Validity}\label{week-06-0301---0305-more-validity}}

\begin{itemize}
\tightlist
\item
  Tuesday: Chapter 6 ``Last day to drop full-term class''
\item
  Thursday: Chapter 9
\end{itemize}

\hypertarget{week-07-0308---0312-item-analysis}{%
\subsection{Week 07, 03/08 - 03/12 : Item
Analysis}\label{week-07-0308---0312-item-analysis}}

\begin{itemize}
\tightlist
\item
  Tuesday: Chapter 7 (Assignment 1 Due)
\item
  Thursday: Chapter 7
\end{itemize}

\hypertarget{week-08-0315---0319-test-1}{%
\subsection{Week 08, 03/15 - 03/19 : Test
1}\label{week-08-0315---0319-test-1}}

\begin{itemize}
\tightlist
\item
  Tuesday: Review
\item
  Thursday: Exam 1
\end{itemize}

\hypertarget{week-09-0322---0326-spring-break}{%
\subsection{Week 09, 03/22 - 03/26 : Spring
Break}\label{week-09-0322---0326-spring-break}}

\begin{itemize}
\tightlist
\item
  Tuesday: No class
\item
  Thursday: No class
\end{itemize}

\hypertarget{week-10-0329---0402-individual-differences}{%
\subsection{Week 10, 03/29 - 04/02 : Individual
Differences}\label{week-10-0329---0402-individual-differences}}

\begin{itemize}
\tightlist
\item
  Tuesday: Selected readings
\item
  Thursday: Chapter 10
\end{itemize}

\hypertarget{week-11-0405---0409-ability-testing}{%
\subsection{Week 11, 04/05 - 04/09 : Ability
Testing}\label{week-11-0405---0409-ability-testing}}

\begin{itemize}
\tightlist
\item
  Monday: Last day to drop with a grade of ``W''
\item
  Tuesday: Chapter 11
\item
  Thursday: Chapter 12
\end{itemize}

\hypertarget{week-12-0412---0416-personality-testing}{%
\subsection{Week 12, 04/12 - 04/16 : Personality
Testing}\label{week-12-0412---0416-personality-testing}}

\begin{itemize}
\tightlist
\item
  Tuesday: Chapter 13
\item
  Thursday: Chapter 13
\end{itemize}

\hypertarget{week-13-0419---0423-measuring-interests-and-attitudes}{%
\subsection{Week 13, 04/19 - 04/23 : Measuring Interests and
Attitudes}\label{week-13-0419---0423-measuring-interests-and-attitudes}}

\begin{itemize}
\tightlist
\item
  Tuesday: Chapter 14
\item
  Thursday: Chapter 14 (Assignment 2 Due)
\end{itemize}

\hypertarget{week-14-0426---0430-other-assessment-techniques}{%
\subsection{Week 14, 04/26 - 04/30 : Other Assessment
Techniques}\label{week-14-0426---0430-other-assessment-techniques}}

\begin{itemize}
\tightlist
\item
  Tuesday: Chapter 15
\item
  Thursday: Chapter 16
\end{itemize}

\hypertarget{week-15-0503---0507-modern-development-and-applications-of-testing}{%
\subsection{Week 15, 05/03 - 05/07 : Modern Development and Applications
of
Testing}\label{week-15-0503---0507-modern-development-and-applications-of-testing}}

\begin{itemize}
\tightlist
\item
  Tuesday: Supplemental reading
\item
  Thursday: Supplemental reading
\end{itemize}

\hypertarget{week-16-0510---0514-review}{%
\subsection{Week 16, 05/10 - 05/14 :
Review}\label{week-16-0510---0514-review}}

\begin{itemize}
\tightlist
\item
  Tuesday: Review
\end{itemize}

\hypertarget{final-exam}{%
\subsection{Final Exam}\label{final-exam}}

\begin{itemize}
\tightlist
\item
  TBD
\end{itemize}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-anastasi1997}{}%
Anastasi, Anne, and A. Urbina. 1997. \emph{Psychological Testing}. Upper
Saddle River, New Jersey: Prentice-Hall.





\end{document}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother
