---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    latex_engine: pdflatex
    template: ./common/style/svm-latex-syllabus.tex
    
bibliography: library.bib

geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt

title: "PSY 362. Psychological Testing"

date: '`r format(Sys.time(), "%B %d, %Y")`'

author: S. Mason Garrison
email: "GarrisSM@wfu.edu"


officehours: By Appointment \href{https://calendly.com/smasongarrison/}{\small\tt calendly.com/smasongarrison}
office: "GREENE 438"
officev: Zoom \href{https://wakeforest-university.zoom.us/my/smasongarrison}{\tiny\tt wakeforest-university.zoom.us/my/smasongarrison}

classroom: Canvas
classdelivery: "Asynchronous"
web: \href{https://wakeforest.instructure.com/courses/28913}{\tt wakeforest.instructure.com/courses/28913} 



header-includes:
   - \linespread{1.05}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
mon <- as.Date("2021-01-25")
cache=F
number_of_classes=29
number_of_weeks=15
advdate <- function(obj, adv, topic = NULL,assignment=NULL) {
 tmon <- obj + 7*(adv-1)
 ttue <- obj + 1 + 7*(adv-1)
 twed <- obj + 2 + 7*(adv-1)
 tthu <- obj + 3 + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 ttue <- format(ttue, format="%m/%d")
 twed <- format(twed, format="%m/%d")
 tthu <- format(tthu, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)

 if (is.null(topic)&is.null(assignment)){
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 } else if(!is.null(assignment)){if(assignment %in% c("Friday","friday","f","fri")){
  tmp <- paste0(tfri)
 } else if(assignment %in% c("Tuesday","tues","t","Tue")){
  tmp <- paste0(ttue)
 }else if(assignment %in% c("wednesday","Wednesday","w","wed","W")){
  tmp <- paste0(twed)
 } else if(assignment %in% c("thursday","Thursday","thurs","r","R")){
  tmp <- paste0(tthu)
 } else if(assignment %in% c("monday","Monday","m")){
  tmp <- paste0(tmon)
 }
 }
 else{ 
   tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri, " : ", topic[adv])}
 return(tmp)
}

####
#devtools::install_github("crsh/citr")
library(tidyverse)
library(citr)
library(RefManageR)



bib <- ReadBib("library.bib")
bib <- c(bib, as.BibEntry(citation()))
bib[length(bib)]$key = "Rcite"

topic=c(
  "Introduction", 
  "Historical, Ethical, and Social Considerations in Testing",
  "Norms and the Meaning of Test Scores",
  "Reliability",
  "Validity",
  "More Validity", 
  "Item Analysis", 
  "Test 1",
  "Spring Break",
  "Individual Differences",
  "Ability Testing",
  "Personality Testing", 
  "Measuring Interests and Attitudes",
  "Other Assessment Techniques", 
  "Modern Development and Applications of Testing", 
  "Review"
  )
  
  



```

# Course Description

This course provides an overview of the development and nature of psychological tests with applications to school counseling, business, and clinical practice. The purpose of the course is to provide students with an understanding of the principles of measurement as applied to group standardized measures of achievement, special aptitude, intelligence, personality, interests and distress for use in counseling.  Format will consist primarily of lectures along with group participation activities. 


## Course Objectives:
- To acquaint you with the fundamental vocabulary and logic of psychological measurement and behavioral assessment.
- To develop your capacity for critical judgment of the adequacy of measures purported to assess behavior in the role of theory development.
- To acquaint you with some of the relevant literature in personality assessment, psychometric theory and practice, and methods of observing and measuring behavior.
- To instill in you an appreciation of and an interest in the principles and methods of psychometric theory in general and behavior assessment in particular.
- This course is not designed to make you into an accomplished psychometist (one who gives tests) nor is it designed to make you a skilled psychometrician (one who constructs tests), nor will it give you "hands on" experience with psychometric computer programs. Rather it is aimed to allow you to understand the fundamental theoretical issues concerning both the psychometrist and the psychometrician.
- Because modern psychometrics and statistics may be done using open source software such as R, examples will be presented in R.

# Materials
## Texts
### Required

```{r, echo = FALSE, results="asis"} 
bib[sort(c("anastasi1997"))]
``` 


#### How to use the required text:

The text [@anastasi1997] is intended to supplement the lectures. The lectures don't follow the order of chapters in the text and the text covers some material that won't be covered in the lectures, i.e., not all the information in each chapter is perfectly pertinent to the course requirements.


# Course Assignments

## Tests 
There will be X tests in this course.  The best 2 out of 3 exam grades will be used to determine your total exam grade.  You can drop any of the exams for any reason BUT YOU MUST PASS THE LAST EXAM (held at TBD on Dec TBD).  If you do not pass the final exam, your score on that exam will count as one of your 2 grades. If you do pass the final exam, then the best 2 grades will be used (irrespective of your score on the final exam).


### Test Dates

- Test 1: Friday, `r advdate(mon, 5, assignment="f")`

- Test 2: Friday, `r advdate(mon, 10, assignment="f")`

- Test 3: During Finals Week


## Short Assignments 
There will be three (3) short assignments in this course. These assignments will allow you to incorporate some of your own interests into the course. Such interests could be related to your career, another class you're taking, a hobby you're exploring, or some other random fancy. They will typically be approximately two (2) pages. I will provide more specific written guidelines at least two weeks before each assignment is due.


The best two (2) out of three (3) short assignments will be used to determine your total short assignments.  You can skip one of the assignments for any reason.
### Short Assignment Dates

- Assignment 1: Friday, `r advdate(mon, 4, assignment="f")`: Critique of an online personality test.

- Assignment 2: Friday, `r advdate(mon, 8, assignment="f")`: Critique of a personality-related media article.

- Assignment 3: Friday, `r advdate(mon, 12, assignment="f")`: Critique of a personality-related YouTube video.

## Engagement Activities

There will be multiple engagement activities in this course. These activities will allow you engage with the material for each module. Details about the specific activities will be provided on canvas. Students must complete two activities per module.



# Course Assignments 
## Grading Policy

```{r child = './common/content/grading.Rmd'}
```

### Grading Weighting

- 200 points of your grade will be determined by two (2) tests.
- 100 points of your grade will be determined by two (2) short assignments.
- 50 points of your grade will be determined by your engagement. Generally, ask questions and answer them.


### Test Dates

- Test 1: Thursday, `r advdate(mon, 8, assignment="t")`

- Test 2: During Finals Week, TBD


## Short assignments 
There will be two (2) assignments in this course. I will provide more specific written guidelines at least two weeks before each assignment is due.


### Short Assignment Dates

- Assignment 1: Tuesday, `r advdate(mon, 7, assignment="t")`.

- Assignment 2: Thursday, `r advdate(mon, 13, assignment="t")`.



# Course Policies

```{r child = './common/content/policies.Rmd'}
```




## `r advdate(mon, 1, topic)`

- Tuesday: Chapter 1
- Thursday: Chapter 2

## `r advdate(mon, 2, topic)`

- Tuesday: Chapter 18
- Thursday: Chapter 18

##  `r advdate(mon, 3, topic)` 

- Tuesday: Chapter 3 "Last day to add full-term class"
- Thursday: Chapter 3

##  `r advdate(mon, 4, topic)`

- Tuesday: Chapter 4
- Thursday: Chapter 4

##  `r advdate(mon, 5, topic)`

- Tuesday: Chapter 5 + 6
- Thursday: Chapter 5 + 6 

##  `r advdate(mon, 6, topic)`

- Tuesday: Chapter 6  "Last day to drop full-term class"
- Thursday: Chapter 9 

##  `r advdate(mon, 7, topic)` 

- Tuesday: Chapter 7 (Assignment 1 Due)
- Thursday: Chapter 7

##  `r advdate(mon, 8, topic)`

- Tuesday: Review 
- Thursday: Exam 1

##  `r advdate(mon, 9, topic)`

- Tuesday: No class
- Thursday: No class 

##  `r advdate(mon, 10, topic)`

- Tuesday: Selected readings
- Thursday: Chapter 10

##  `r advdate(mon, 11, topic)`

- Monday: Last day to drop with a grade of "W"
- Tuesday: Chapter 11
- Thursday: Chapter 12

##  `r advdate(mon, 12, topic)`

- Tuesday: Chapter 13
- Thursday: Chapter 13 

## `r advdate(mon, 13, topic)`

- Tuesday: Chapter 14
- Thursday: Chapter 14 (Assignment 2 Due)

##  `r advdate(mon, 14, topic)`

- Tuesday: Chapter 15
- Thursday: Chapter 16

##  `r advdate(mon, 15, topic)`

- Tuesday: Supplemental reading
- Thursday: Supplemental reading

##  `r advdate(mon, 16, topic)` 

- Tuesday: Review

## Final Exam 

- TBD

# References
