---
output: 
  pdf_document:
    keep_tex: no
    fig_caption: yes
    latex_engine: pdflatex
    template: ./common/style/svm-latex-syllabus.tex
    
bibliography: library.bib

geometry: margin=1in

title: "PSY-703: Data Science for Psychologists"

date: '`r format(Sys.time(), "%B %d, %Y")`'

author: S. Mason Garrison
email: "GarrisSM@wfu.edu"



officehours: By Appointment \href{https://calendly.com/smasongarrison/}{\small\tt calendly.com/smasongarrison}
office: "GREENE 438"
officev: Zoom \href{https://wakeforest-university.zoom.us/my/smasongarrison}{\tiny\tt wakeforest-university.zoom.us/my/smasongarrison}

sectionA: Monday
sectionB: Friday
classroomA: GREENE ###
classhoursA: "M @ 9:30a-10:50a"
classdeliveryA: "Blended"
classroomB: GREENE ###
classdeliveryB: "Blended"
classhoursB: "F @ 9:30a-10:50a"
web: \href{https://datascience4psych.github.io/DataScience4Psych/}{\tt datascience4psych.github.io/DataScience4Psych/}
git: \href{https://github.com/DataScience4Psych/DataScience4Psych}{\tt github.com/DataScience4Psych/DataScience4Psych}
fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
---
<!-- 
classroom: "GREENE 160"
classhours: "MWF 9:00a-9:50a"
canvas: \href{https://wakeforest.instructure.com/courses/29807}{\tt wakeforest.instructure.com/courses/29807}

---> 
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='pdf')
mon <- as.Date("2021-01-25")
cache=F
number_of_classes=29
number_of_weeks=15
advdate <- function(obj, adv, topic = NULL,assignment=NULL) {
 tmon <- obj + 7*(adv-1)
 ttue <- obj + 1 + 7*(adv-1)
 twed <- obj + 2 + 7*(adv-1)
 tthu <- obj + 3 + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 ttue <- format(ttue, format="%m/%d")
 twed <- format(twed, format="%m/%d")
 tthu <- format(tthu, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)

 if (is.null(topic)&is.null(assignment)){
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 } else if(!is.null(assignment)){if(assignment %in% c("Friday","friday","f","fri")){
  tmp <- paste0(tfri)
 }else if(assignment %in% c("wednesday","Wednesday","w","wed","W")){
  tmp <- paste0(twed)
 } else if(assignment %in% c("monday","Monday","m")){
  tmp <- paste0(tmon)
 }
 }
 else{ 
   tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri, " : ", topic[adv])}
 return(tmp)
}

####
#devtools::install_github("crsh/citr")
library(tidyverse)
library(citr)
library(RefManageR)



bib <- ReadBib("library.bib")
bib <- c(bib, as.BibEntry(citation()))
bib[length(bib)]$key = "Rcite"



topic_vjoe=c(
  "Introduction and What is Data Science", 
  "Graphical Data Analysis",
  "Graphical Masterpieces",
  "Scatterplots and Correlations",
  "Quiz 1",
  "Exploratory Data Analysis",#  "Spring Break",#  "",
  "Data Transformations", 
  "Robustness and Resistence", 
  "Replication",
  "Quiz 2",
  "Modern Data Science", 
  "Archival Data", 
  "Data mining and CART",
  "Special Topics",
  "Special Topics" 
  )








topic=c(
  "What is Data Science and Meet the Toolkit", 
  "Data and Visualization",
  "Grammar of data wrangling",
  "Data types and Data Transformations",
  "Tips for effective data visualization",
  "Scientific studies and confounding",#  "Spring Break",#  "",
  "Web scraping", 
  "Functions", 
  "Data and Ethics",
  "Fitting and interpreting models",
  "Prediction and overfitting", 
  "Cross validation", 
  "Quantifying uncertainty",
  "Special Topics (like: Text analysis; Interactive web apps; Machine learning; Bayesian inference",
  "Special Topics" 
  )



```



# Course Description

Data Science for Psychologists (DSP) introduces on the principles of data science, including data wrangling, modeling, visualization, and communication. In this class, we link those principles to psychological methods and open science practices by emphasizing exploratory analyses and description, rather than confirmatory analyses and prediction. We'll work our way thru Wickham and Grolemund's R for Data Science text (http://r4ds.had.co.nz/) and develop expertise in tidyverse (https://www.tidyverse.org/). This class emphasizes replication and reproducibility. DSP is a practical skilled-based class and should be useful to students aiming for academia as well as those interested in industry. Applications of these methods can be applied to a full range of psychological areas, including perception (e.g, eye-tracking data), neuroscience (e.g., visualizing neural networks), and individual differences (e.g., valence analysis).

<!---
```{r child = './common/content/doingwell_irl.Rmd'}
```
--->

## Broad goals for the course:
- 1. Reproducibility;
- 2. Replication;
- 3. Robust Methods;
- 4. Really Nice Visualization; and
- 5. R.

# Required Materials

```{r, echo = FALSE, results="asis", include=FALSE} 
bib[sort(c("funder_personality_2016"))]
``` 

Wickham and Grolemund's R for Data Science text (http://r4ds.had.co.nz/)



### How to use the required text:

The text is intended to supplement the lectures. The lectures don't follow the order of chapters in the text and the text covers some material that won't be covered in the lectures, i.e., not all the information in each chapter is perfectly pertinent to the course requirements.


# Course Assignments

<!---
You will be formally evaluated in five different ways.



## Individual data Project

You will turn in your individual data collection/data analysis projects on Wednesday, September 18.  These projects are described in a separate handout. This project will be worth 10% of your grade.

## Quiz
There will be two 30-minute quizzes over lecture material and readings (on September 25 and October 30).  These will be objective style quizzes.  Make-ups will only be given under extraordinary circumstances and by prior arrangement. Each quiz = 10% of your grade.
-->

## Presentations
You will give two asynchronous presentations.  Your team will give a 15-20 minute presentation of its data analysis problem.  In addition, you will give a 15- minute individual presentation.  These presentations are chance to practice a formal presentation in a relatively pressure-free setting).

## Assignments

<stuff about these should be in here>

## Portfolio
The major semester projects (described on the separate hand-out) is a set of EDA Projects, which you will summarize in an EDA Portfolio to be handed in on the last day of class.


<!---
### Quiz Dates

- Quiz 1: Friday, `r advdate(mon, 5, assignment="f")`

- Quiz 2: Friday, `r advdate(mon, 10, assignment="f")`

-->

## Engagement

This experiential course requires active engagement. There will be few lectures and we will not be building toward an exam.  Instead, we will work together to build our facilities for thinking critically about data. You should come to every class having read all of the required reading, watched the required videos, browsed the suggested resources, and so forth. You should enter the classroom prepared to discuss these materials with colleagues and complete both individual and group in-class assignments.

<!---

### Activities

Because this class is blended, there will be multiple online engagement activities. These activities will allow you engage with the material for each module. Details about the specific activities will be provided on canvas.

-->

# Grading Policy

```{r child = './common/content/contract.Rmd'}
```


## Contract Grades


```{r child = './common/content/contract_grades_ds4p.Rmd'}
```


<!---
- 200 points of your grade will be determined by your best two exams.
    - The final is not optional.
- 50 points of your grade will be determined by completing engagement activities.

your attendance and participation in engagement activities. Generally, ask questions and answer them.

- 100 points of your grade will be determined by your best two short assignments.
-->




# Course Policies

```{r child = './common/content/policies.Rmd'}
```

<!---
Schedule
-->

## `r advdate(mon, 1, topic)`
<!---
- Monday: First Day of Class / Introduction
- Wednesday: What is personality? (Chapter 1)
- Friday: Research in Personality: Sources of Data (Chapter 2)
-->
## `r advdate(mon, 2, topic)`
<!---
- Monday: NO CLASS MLK Day
- Wednesday: Research Design: Validity (Chapter 2)
- Friday: Research Design: Generalizability (Chapter 2; Short Assignment 1 Handed Out)
-->
##  `r advdate(mon, 3, topic)` 
<!---
- Monday: Personality Assessment (Chapter 3)
- Tuesday: "Last day to add full-term class"
- Wednesday: Evaluation and Ethics (Chapter 3)
- Friday: Person versus Situation (Chapter 4)
-->

##  `r advdate(mon, 4, topic)`
<!---
- Monday: What are traits? What are the basic traits? (Chapter 4)
- Wednesday: Personality Judgement (Chapter 5)
- Friday: Using Personality Traits to Understand Behavior (Chapter 6; Assignment 1 Due)
-->
##  `r advdate(mon, 5, topic)`
<!---
- Monday: Big Five (Chapter 6)
- Wednesday: Review
- Friday: Test 1
-->
##  `r advdate(mon, 6, topic)`
<!---
- Monday: Brains (Chapter 8)
- Wednesday: More Brains (Chapter 8)
- Friday: Behavior Genetics (Chapter 9)
-->
##  `r advdate(mon, 7, topic)` 
<!---
- Monday: Behavior Genetics (Chapter 9)
- Wednesday: Evolutionary Psychology (Chapter 9)
- Friday: Evolutionary Psychology (Chapter 9)
-->
##  `r advdate(mon, 8, topic)`
<!---
- Monday: Personality over the Lifespan (Chapter 7)
- Wednesday: Personality over the Lifespan (Chapter 7)
- Friday: Personality Processes (Chapter 15)
-->
##  `r advdate(mon, 9, topic)`
<!---
- Monday: No Class
- Wednesday: No Class
- Friday: No Class
-->
##  `r advdate(mon, 10, topic)`
<!---
- Monday: Personality Processes (Chapter 15)
- Wednesday: Review
- Friday: Test 2
-->
##  `r advdate(mon, 11, topic)`
<!---
- Monday: The Self (Chapter 16) Last day to drop with a grade of "W"
- Wednesday: The Self (Chapter 16)
- Friday:  Freud (Chapter 10) 
-->
##  `r advdate(mon, 12, topic)`
<!---
- Monday: Freud (Chapter 10)
- Wednesday: Freud (Chapter 10)
- Friday: Neo-Freud (Chapter 11; Assignment 2 Due)
-->
## `r advdate(mon, 13, topic)`
<!---
- Monday:  Neo-Freud (Chapter 11) 
- Wednesday: Positive Psychology
- Friday: Positive Psychology
-->
##  `r advdate(mon, 14, topic)`
<!---
- Monday: Cross-Cultural Psychology
- Wednesday: Cross-Cultural Psychology
- Friday: Cross-Cultural Psychology
-->

##  `r advdate(mon, 15, topic)`
<!---
- Monday: Personality and Physical Health
- Wednesday: Personality and Mental Health
- Friday: Personality Disorders

##  `r advdate(mon, 16, topic)` 

- Monday: Special Topics
- Wednesday: Review; Assignment 3 Due; Last Day of Class

## Final Exam 

- TBD on DEC TBD
-->
# References